Untitled

### 2023-09-09 code/analysis_Redo.Rmd
more adjustments

df.size <- df.size %>% 
  left_join(dfc %>% filter(Year == 2010) %>% select(ID, Total) %>% 
  mutate(Size = Total) , by = c("ID")) # %>% filter(`BHCMIS ID` %notin% c("010450","070430"))

@@

df.liquid <- df.liquid %>% 
  left_join(dfc %>% filter(Year == 2010) %>% select(ID, quick_ratio) %>% 
  mutate(liquid = quick_ratio) , by = c("ID")) # %>% filter(`BHCMIS ID` %notin% c("010450","070430"))

@@

>>>>

df.size <- df.size %>% 
  left_join(dfc %>% filter(year.rel == -1) %>% select(ID, Total) %>% 
  mutate(Size = Total) , by = c("ID")) # %>% filter(`BHCMIS ID` %notin% c("010450","070430"))

@@

df.liquid <- df.liquid %>% 
  left_join(dfc %>% filter(year.rel == -1) %>% select(ID, quick_ratio) %>% 
  mutate(liquid = quick_ratio) , by = c("ID")) # %>% filter(`BHCMIS ID` %notin% c("010450","070430"))

@@

did2s(
      data = df.liquid %>% filter(!is.na(liquid)) , 
      yname = "Qcomp", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * liquid) + I(Tx * liquid^2) ,
        cluster_var = "STATE",
      verbose = FALSE
    )
```
